Introduction Concurrent Programming with CXL

### 2020-05-15 book/paper.tex
Latest

Before we delve into how to solve synchronization problems, it is important
to know a bit about the underlying machine.  A CXL program is translated
into a list of machine instructions that the machine executes.
The CXL machine is not an ordinary virtual machine, but its architecture
is nonetheless representative of conventional machines such as hardware CPUs
and virtual machines such as the Java Virtual Machine.

A CXL machine has the following components:
\begin{itemize}
\item The code.  This is an immutable list of CXL machine instructions.  The
instructions will be described later.
\item The memory.  This is a tree-shaped recursive data structure.  Each node
in the tree, including the leaves and the root, are \emph{CXL values}.  CXL
values include booleans, integers, strings, sets of CXL values, and, importantly
\emph{dictionaries} that maps CXL values to other CXL values.
The root of the tree is a dictionary that maps strings to CXL values.
\item The set of processes.  Initially there is just the main process, but any process
can spawn an unbounded number of other processes and processes may terminate.
Each process has an immutable
tag, a stack of CXL values, and a mutable \emph{register}, which contains a
dictionary that maps strings to CXL values.
\end{itemize}

>>>>

Before we delve into how to solve synchronization problems, it is important
to know a bit about the underlying machine.  A CXL program is translated
into a list of machine instructions that the machine executes.
The CXL machine is not an ordinary virtual machine, but its architecture
is nonetheless representative of conventional machines such as hardware
with memory and CPUs and virtual machines such as the Java Virtual Machine.

Instead of bits and bytes, a CXL machine manipulates \emph{CXL values}.
CXL values are recursively defined: they include booleans, integers, strings,
sets of CXL values, and \emph{dictionaries} that map CXL values to other CXL
values.

A CXL machine has the following components:
\begin{itemize}
\item Code:  This is an immutable list of CXL machine instructions.  The
instructions will be described later.
\item Shared memory: A CXL machine has just one memory location containing
a CXL.
\item Processes:  Initially there is just the main process, but any process
can spawn an unbounded number of other processes and processes may terminate.
Each process has an immutable tag, a program counter, a stack of CXL values,
and a single mutable general purpose \emph{register} that contains a CXL.
\end{itemize}

The state of a process is called a \emph{context}: it contains the value of
its program counter, stack, and register.  The state of the CXL machine
consists of the value of its memory and the multiset (or \emph{bag}) of
contexts.  It is a multiset of contexts because two different processes can
be in the same state.

It may seem strange that there is only one memory location and that each
process has only one register.  However, this is not a limitation because
CXL values are unbounded trees.
By convention, both the memory and the register of a process always contain
a special type of CXL value in which the root is a dictionary
that maps strings to CXL values.  It represents the state of a collection of
variables named by the strings.
